---
title: A03 Working with Data in the Tidyverse
author: MonaJzn
date: '2021-06-04'
slug: a03-working-with-data-in-the-tidyverse
categories:
  - tidyvers
tags: []
---
## Import lego_sales.csv file
```{r}
library(tidyverse)
lego <- read_csv(file = "lego_sales.csv")
lego <- read_csv(file.choose())
head(lego)
```
## What are the three most common first names of customers?
```{r}
lego %>%
  count(first_name, sort = TRUE)
```
Jackson, Jacob, and Joseph are the three most common first names.

## What are the three most common themes of lego sets purchased?
```{r}
lego %>%
  count(theme, sort = TRUE)
```
Star Wars, Nexo Knights, and Gear are the three most common themes.

## Among the most common theme of lego sets purchased, what is the most common subtheme?
```{r}
lego %>%
  filter(theme == "Star Wars" | theme == "Nexo Knights" | theme == "Gear") %>%
  count(subtheme, sort = TRUE)
```
Ultimate is the most common subtheme among the most common theme of lego sets.

## Create a new variable called age_group and group the ages into the following categories: “18 and under”, “19 - 25”, “26 - 35”, “36 - 50”, “51 and over”. Be sure to save the updated data set so you can use the new variable in other questions.
```{r}
lego_age <- lego %>%
  mutate(age_group = case_when(between(age, 1, 18) ~ "18 and under", between(age, 19, 25) ~ "19 - 25", between(age, 26, 35) ~ "26 - 35", between(age, 36, 50) ~ "36 - 50", between(age, 51, 68) ~ "51 and over"))
age <- lego_age %>%
  select(first_name, last_name, age_group)
age
```
## What is the probability a randomly selected customer
## is in the 19 - 25 age group?
```{r}
lego_age %>%
count(age_group == "19 - 25")/nrow(lego_age)

```
Answer: 0.208

## is in the 19 - 25 age group and purchased a Duplo theme set?
```{r}
lego_age %>%
count(age_group == "19 - 25" & theme == "Duplo")/nrow(lego_age)

```
Answer: 0.0145

## is in the 19 - 25 age group given they purchased a Duplo theme set?
```{r}
lego_age_d <- lego_age %>%
  filter(theme == "Duplo") 
```
```{r}
lego_age %>%
filter(theme == "Duplo") %>%
count(age_group == "19 - 25")/nrow(lego_age_d)

```


Answer: 0.257

## Which age group has purchased the largest number of lego sets? How many did they purchase?

```{r}
lego_age_q <- lego_age %>%
  group_by(age_group) %>%
 summarize(s = sum(quantity))

lego_age_q
```
Age group "36 - 50" has purchased the largest number of lego sets which is 313.

## Which age group has spent the most money on legos? How much did they spend?
```{r}
lego_age_spend <- lego_age %>%
  mutate(spend = us_price * quantity) %>%
  arrange(desc(spend))
lego_age_spend
```
26 - 35 age group has spent the most money on legos, $699.98.

## Come up with a question you want to answer using this data, and write it down. Then, create a data visualization that answers the question, and briefly explain how your visualization answers the question.

## Which age group has spend the most on Star Wars theme?
```{r}

lego_age_s <- lego_age_spend %>%
  filter(theme == "Star Wars")

  ggplot(lego_age_s, aes(age_group, spend)) +
  geom_col(fill = "red")
   
```
Age group 26-35 has purchased the most pieces of lego sets, almost 8000 pieces of star wars theme.


## Add one element to the plot from the previous exercise to change the look of the plot without changing the underlying data. For example, you can change the theme, background color, add annotations, etc. State the change you’re making and display the updated visualization. We encourage you to be creative!


```{r}
  lego_age_s <- lego_age_spend %>%
  filter(theme == "Star Wars")

  ggplot(lego_age_s, aes(age_group, spend)) +
  geom_col(alpha = 0.6, fill = "green") +
  theme_minimal() +
  labs(
    x = "Age group", y = "Spend", 
    title = "Total puchase amount of starwars theme purchased by each age group" 
        )
```
I added minimal theme and labels for title, x axis, and y axis.



